\begin{thebibliography}{10}

\bibitem{andreas2} KIEFER, Andreas; DUARTE, Elias P. Jr; MURTA, Cristina D. \textbf{Monitoring Multiple Concurrent Service Level Parameters with Multidimensional Trees}. The 20th IEEE/IFIP International Workshop on Distributed Systems Operations and Management (DSOM), Lecture Notes in Computer Science 5841, pp. 1-14, Venice, Italy, 2009. 

\bibitem{andreas} KIEFER, Andreas. \textbf{Gerência de Desempenho Baseada em Pesquisa Multidimensional}. Curitiba: UFPR, 2004. Dissertação (Mestrado) - Programa de Pós-Graduação em Informática, Universidade Federal do Paraná, Curitiba, 2004.

\bibitem{ziviani} ZIVIANI, Nivio. \textbf{Projeto de Algoritmos: com Implementações em Pascal e C}. 2. ed. - Thomson Learning, 2004.

\bibitem{bentley} BENTLEY, J. L. \textbf{Multidimensional Binary Search Trees Used For Associative Searching}. Communications of the ACM, 1975.

\bibitem{bentley2} BENTLEY, J. L. \textbf{Multidimensional Binary Search in Database Applications}. IEEE Transactions on Software Engineering, 1979.

\bibitem{bentley3} BENTLEY, J. L.; FRIEDMAN, J. H. \textbf{Data Structures for Range Searching}. ACM Computing Surveys, 1979.

\bibitem{comer} COMER, D. E. \textbf{The Ubiquitous B-tree}. ACM Compt. Surv., 1979.

\bibitem{robinson} ROBINSON, J. T. \textbf{The K-D-B-Tree: A Search Structure for Large Multidimensional Dynamic Indexes}. Y. Edmund Lien, editor, Proceedings of the 1981 ACM SIGMOD
International Conference on Management of Data, Ann Arbor, Michigan, April 29 - May 1, 1981, pp. 10¿18. ACM Press, 1981.

\bibitem{guttman} GUTTMAN, A. \textbf{R-Trees: A Dynamic Index Structure for Spatial Searching}. Annual Meeting ACM SIGMOD. Boston, MA, 1984. p. 47-57

\bibitem{gonnet} GONNET, H. G.; BAEZA-YATES, R. \textbf{Handbook of Algorithms and Data Structure: in Pascal and C}. Addison-Wesley Publishing Company, Inc., 2nd edition, 1991.

\bibitem{libkdtree} \textbf{libkdtree++} Disponível em: http://libkdtree.alioth.debian.org/ Acesso em: nov. 2009.

\bibitem{tpie} \textbf{TPIE} Disponível em: http://www.cs.duke.edu/TPIE/ Acesso em: nov. 2009.

\bibitem{sunmysql} \textbf{MySQL} Disponível em: http://www.sun.com/software/products/mysql/index.jsp Acesso em: set. 2009.

\bibitem{indicesMysql} \textbf{MySQL} Disponível em: http://dev.mysql.com/doc/refman/4.1/pt/mysql-indexes.html Acesso em: set. 2009.

\bibitem{gilberg} GILBERG, R. e FOROUZAN, B. \textbf{Data Structures: A Pseudocode Approach With C++}. Pacific Grove, CA: Brooks/Cole, 2001.

\bibitem{gaede} GAEDE, V. e GUNTHER O. \textbf{Survey on Multidimensional Access Methods (Revised Version)}. ACM Computing Surveys, 1998.

\bibitem{bancodedados} \textbf{Banco de Dados} Disponível em : www.ime.usp.br/~jef/apostila.pdf Acesso em: out. 2009.

\bibitem{mysqlLIF} \textbf{MySQL: LOAD IN FILE} Disponível em : http://dev.mysql.com/doc/refman/4.1/pt/insert-speed.html Acesso em: out. 2009.

\bibitem{StorageEngine} \textbf{Storage Engine} Disponível em :  http://dev.mysql.com/doc/refman/5.1/en/storage-engines.html Acesso em: out. 2009.

\bibitem{NetworkManagement} LEINWAND, A.; CONROY, K. F. \textbf{Network Management: A Practical Perspective}. Addison-Wesley Publishing Company, Inc., 2nd edition, 1996.

\bibitem{Abraham} SILBERSCHATZ, ABRAHAM; KORTH, HENRY F. e SUDARSHAN, S. \textbf{Sistema de Banco de Dados}. MAKRON Books, 3ª edição, 1996.

\bibitem{LoadDataInfile} \textbf{Load data Infile} Disponível em :  http://dev.mysql.com/doc/refman/5.1/en/load-data.html Acesso em: nov. 2009.

\bibitem{GerenciaRede} Lopes, R. V.; SAUVÉ, J. P.; NICOLLETTI P. S. \textbf{Gerência de Redes de Computadores}. Editora Campus, 2003.

\bibitem{sla} IEC. \textbf{Carrier Service-Levels Agreements (SLAs)} Disponível em: http://www.iec.org/online/tutorials/carrier\_sla/index.asp Acesso em: nov. 2009.

\bibitem{snmp} PRESUHN, R. \textbf{Version 2 of the Protocol Operations for the Simple Network Management Protocol (SNMP)}, Request for Comments 3416, 2000.

\bibitem{tcpip} COMER, D. E. \textbf{Internetworking with TCP/IP: Principles, Protocols and Architecture}, volume1. Prentice Hall, 4th edition, 2000.

\end{thebibliography}
